Northern Pikeminnow Predation on Juvenile Chinook Salmon in Deadwater Slough, Salmon River, Idaho and Potential Impacts to Local Populations

### 2022-01-14 analysis/paper/paper.Rmd
added code to examine if marked fish weren't available for recapture until 2 days after capture.

```{r abund-est}
all_est = LP_mod %>%
  select(event_name, species, model, N:Uci) %>%
  bind_rows(N_mods %>%
             select(event_name, species, model, N:Uci)) %>%
  mutate(range = Uci - Lci,
         prop_range = range / N) %>%
  mutate(across(event_name,
                ~ str_replace(., "_", " "))) %>%
  mutate(model = fct_recode(model,
                            "Schumacher-Eschmeyer" = "SchumacherEschmeyer"),
         model = fct_relevel(model,
                             "Petersen",
                             after = 0)) %>%
  arrange(event_name, model)

>>>>

```{r assump-violation}
# assume that marked fish aren't available for recapture until 2 days after capture
# using Schnabel estimator
N_mods_viol = N_mods %>%
  filter(model == "Schnabel") %>%
  select(event_name:model) %>%
  mutate(data = map(data,
                    .f = function(x) {
                      x %>%
                        mutate(R_lag = lag(R),
                               R_lag = replace_na(R_lag,
                                                  0))
                    })) %>%
  mutate(mr_model = map2(data,
                         model,
                         .f = function(x, y) {
                           with(x,
                                mrClosed(n = n,
                                         m = m,
                                         R = R_lag,
                                         method = y,
                                         chapman.mod = TRUE))
                         }),
         N = map_dbl(mr_model,
                     .f = summary),
         CI = map(mr_model,
                  .f = confint),
         Lci = map_dbl(CI,
                       .f = function(x) x[1]),
         Uci = map_dbl(CI,
                       .f = function(x) x[2])) %>%
  ungroup() %>%
  select(-CI) %>%
  mutate(model = "Schnabel - Delayed Mixing")
```

```{r abund-est}
all_est = LP_mod %>%
  select(event_name, species, model, N:Uci) %>%
  bind_rows(N_mods %>%
             select(event_name, species, model, N:Uci)) %>%
  bind_rows(N_mods_viol %>%
             select(event_name, species, model, N:Uci)) %>%
  mutate(range = Uci - Lci,
         prop_range = range / N) %>%
  mutate(across(event_name,
                ~ str_replace(., "_", " "))) %>%
  mutate(model = fct_recode(model,
                            "Schumacher-Eschmeyer" = "SchumacherEschmeyer"),
         model = fct_relevel(model,
                             "Petersen",
                             after = 0)) %>%
  arrange(event_name, model) %>%
  filter(! model %in% c("Petersen",
                        "Schumacher-Eschmeyer"))
